\section{Overview}
\setlength{\parindent}{10ex}

Sea floor topography is critically important for Earth's natural processes and mankind.
It influences ocean circulation, helps moderate Earth's climate, and effects the biological diversity of the sea \cite{kunze2004role}.
Accurate mapping of sea floor topography is also of great interest to national defense \cite{goodman1982defence}.
With applications in \ac{ASW}, \ac{MIW}, and the general Naval Fleet, along with being important to the shipping and commercial maritime industries.

\par
Despite the importance of sea floor topography to all, mankind has produced much better maps of other planets, moons, and asteroids than Earth's sea floor \cite{becker2009global}.
Earth's oceans are vast and deep which makes accurate bathymetry measurement techniques like \ac{SDB} impossible for the majority of the ocean.
Unknown sediment composition and other environmental features limit the global accuracy of gravitational regression models to \~{}200 meters.
As of 2009, it is estimated that \~{}90 percent of Earth's oceans remains inaccurately mapped at a high resolution \cite{becker2009global}.

\par
Therefore, improving existing bathymetry prediction techniques is of great interest to many domains.
Coastal predictions can be performed at very high accuracies, but are unable predict depths greater than ~50 meters.
Previous works as described in the Literature Review chapter have improved existing physics models using aggregation, optimization, and \ac{ML}.
Each work is based upon improving the existing physics model.
These models have not been historically accurate enough to predict bathymetry at a fine resolution.

\par
In this work, I contribute to this domain by experimenting with fitting \ac{ML} models for predicting global bathymetry.
My experimentation uses a set of ocean features for training.
These experiments are performed to identify new approachs for predicting bathymetry that contrast to the current physics based models.
Initially,  my work focused on fitting a regression model for predictions.
However, poor results and analysis indicated other approaches to be worth attempting.
This lead to a conversion to a classification problem.
Analysis of the classification results indicated that model decision surfaces differed across geophysical locations, environmental factors, and depth.
These results were tested with a experiment to test model success across different areas of the Earth.
Using these results, I constructed a novel classifier by injecting the most accurate model before prediction.
The \textit{Grid Optimized Model Injector Classifier} increases the accuracy of the resulting model and suggests that localized selections can be made to achieve accurate predictions.